pema application

### 2022-12-05 paper/manuscript.Rmd
fix description lasso

The BRMA method introduced here offers both LASSO and regularized horseshoe priors.
The LASSO prior is given by:
\begin{align}
\beta_{j} &\sim \text{DE}(0, \frac{s}{\lambda})\\ (\#eq:lasso)
\lambda &\sim \chi^2(0, \nu_1)
\end{align}
where DE denotes the double exponential distribution centered around zero,
with a scale determined by a global scale parameter $s$ that is multiplied by the inverse of tuning parameter $\lambda$.
Increasing the scale parameter extends the prior to cover more extreme values.
The inverse tuning parameter is estimated from the data 
by assigning it a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$ [@vanErpOberskiMulder2019].
Increasing the degrees of freedom assigns greater probability mass to extreme values, resulting in less regularization.
The present study used default values for the prior parameters,
$s = 1$, $\nu_1 = 1$, as suggested by @vanErpOberskiMulder2019.

>>>>

The BRMA method introduced here offers both LASSO and regularized horseshoe priors.
The LASSO prior is given by:
\begin{align}
\beta_{j} &\sim \text{DE}(0, \frac{s}{\lambda})\\ (\#eq:lasso)
\frac{1}{lambda} &\sim \chi^2(0, \nu_1)
\end{align}
where DE denotes the double exponential distribution centered around zero,
with a scale determined by a global scale parameter $s$ that is multiplied by the inverse of tuning parameter $\lambda$.
Increasing the scale parameter extends the prior to cover more extreme values.
The inverse tuning parameter is estimated from the data 
by assigning it a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$.
Increasing the degrees of freedom assigns greater probability mass to extreme values, resulting in less regularization.
The present study used default values for the prior parameters,
$s = 1$, $\nu_1 = 1$, which are the same defaults as used in `brms` [@R-brms_a].
